Syntactically Informed Natural Language Inference

### 2019-03-18 cse517/report/main.tex
Updating report

\title{CSE 517: Project Proposal}

@@

\begin{document}
\maketitle

@@

We intend to extend the DA model and evaluate new models on SNLI, MultiNLI
\citep{Williams2017-uh}, the SNLI and MultiNLI hard splits
\citep{Gururangan2018-lj}, and smaller, domain specific datasets like Scitail
\citep{Khot2018-th}.

@@

\section{Previous Work}

>>>>

\newcommand{\dpcomment}[1]{\textcolor{green}{[#1 --deric]}}
\newcommand{\jbcomment}[1]{\textcolor{orange}{[#1 --josh]}}

\title{Syntactically Informed Natural Language Inference}

@@

\begin{document}
\maketitle
\begin{abstract}
  Abstract.
\end{abstract}

@@

@@

We extend the DA model by encorporating syntactic features.
\dpcomment{Include brief summary of constributions here.}
We primarily
evaluate on the domain specific Scitail \citep{Khot2018-th} for both its
smaller size and lack of annotation artifacts when compared to SNLI
\citep{Gururangan2018-lj}.

\section{Syntactic Entailment}
